MTBD models with partner notification

### 2023-06-05 article/article.tex
BDPN estimator and simulation pipelines

\begin{equation}
\scriptsize
\begin{cases}
\dot{p}_{s,si}^{(i,o)}(t) = & \Big(\sum\limits_{k=1}^{m} \mu_{sk} + \sum\limits_{k=1}^{m} \lambda_{sk} + \psi_s\Big) p_{s,si}^{(i)}(t)\; \textit{\color{gray} $\leftarrow$ no event in the next infinitesimal time $\Delta t$ }\\
    & - \sum\limits_{k=1}^{m} \mu_{sk} p_{k,si}^{(i,o)}(t)\;  \textit{\color{gray} $\leftarrow$ change of the state, folowed by evolution from the new state }\\
    & - \sum\limits_{k=1}^{m} \lambda_{sk} p_{s,si}^{(i,o)}(t)U_{k}(t)\;  \textit{\color{gray} $\leftarrow$ transmission, where the recipient subtree stayed unsampled}\\
p_{s,si}^{(i,o)}(t_i) = & 
    \begin{cases}
    0 & \textit{\color{gray} if $i$ is in state $k \neq si$}\\
    1 & \textit{\color{gray} if $i$ is in state $si$}
    \end{cases}\label{eq:p-o}
\end{cases}
\end{equation}

@@

For a tip $i$ whose branch starts at time $t_j$ and finishes at time $t_i$, these values can be calculated as:
\begin{equation}
\scriptsize
\begin{array}{ll}
l^{(u)}(i) &= p^{(i)}(t_j)\psi\rho (1-\rho_{n})\\
l^{(n)}(i) &= p^{(i,nh)}(t_j)\psi\rho \rho_{n}\\
l^{(p)}(i, r) &= p^{(r,o)}(t_j)e^{-\psi_n (t_i - t_j)}\psi_{n}\\
\end{array}
\end{equation}

@@

For a tip $i$ whose branch starts at time $t_j$ in state $s \in \{E, I\}$ and finishes at time $t_i$ in state $I$, these values can be calculated as:
\begin{equation}
\scriptsize
\begin{array}{ll}
l^{(u)}_{s}(i) &= p_s^{(i)}(t_j)\psi\rho (1-\rho_{n})\\
l^{(n)}_{s}(i) &= p_s^{(i,nh)}(t_j)\psi\rho \rho_{n}\\
l^{(p)}_{s}(i, r) &= p_s^{(r,o)}(t_j)e^{-\psi_n (t_i - t_j)}\psi_{n}\\
\end{array}
\end{equation}

>>>>

\begin{equation}
\scriptsize
\begin{cases}
\dot{p}_{s,si}^{(i,o)}(t) = & \Big(\sum\limits_{k=1}^{m} \mu_{sk} + \sum\limits_{k=1}^{m} \lambda_{sk} + \psi_s\Big) p_{s,si}^{(i,o)}(t)\; \textit{\color{gray} $\leftarrow$ no event in the next infinitesimal time $\Delta t$ }\\
    & - \sum\limits_{k=1}^{m} \mu_{sk} p_{k,si}^{(i,o)}(t)\;  \textit{\color{gray} $\leftarrow$ change of the state, folowed by evolution from the new state }\\
    & - \sum\limits_{k=1}^{m} \lambda_{sk} p_{s,si}^{(i,o)}(t)U_{k}(t)\;  \textit{\color{gray} $\leftarrow$ transmission, where the recipient subtree stayed unsampled}\\
p_{s,si}^{(i,o)}(t_i) = & 
    \begin{cases}
    0 & \textit{\color{gray} if $i$ is in state $k \neq si$}\\
    1 & \textit{\color{gray} if $i$ is in state $si$}
    \end{cases}\label{eq:p-o}
\end{cases}
\end{equation}

@@

For a tip $i$ whose branch starts at time $t_j$ and finishes at time $t_i$, these values can be calculated as:
\begin{equation}
\scriptsize
\begin{array}{ll}
l^{(u)}(i) &= p^{(i)}(t_j)\psi\rho (1-\rho_{n})\\
l^{(n)}(i) &= p^{(i,nh)}(t_j)\psi\rho \rho_{n}\\
l^{(p)}(i, r) &= p^{(r,o)}(t_j)e^{-\psi_n (t_i - t_r)}\psi_{n}\\
\end{array}
\end{equation}

@@

For a tip $i$ whose branch starts at time $t_j$ in state $s \in \{E, I\}$ and finishes at time $t_i$ in state $I$, these values can be calculated as:
\begin{equation}
\scriptsize
\begin{array}{ll}
l^{(u)}_{s}(i) &= p_s^{(i)}(t_j)\psi\rho (1-\rho_{n})\\
l^{(n)}_{s}(i) &= p_s^{(i,nh)}(t_j)\psi\rho \rho_{n}\\
l^{(p)}_{s}(i, r) &= p_s^{(r,o)}(t_j)e^{-\psi_n (t_i - t_r)}\psi_{n}\\
\end{array}
\end{equation}
